A universal standard archive file for adsorption data

### 2020-11-30 manuscript/article.tex
first draft somewhat complete

This simple program will parse the output data to find data items detailed in the AIF dictionary.
These data items are converted to the appropriate units and the isotherm is split into the adsorption and desorption parts.
Subsequently an AIF is produced using the pymatgen CIF routines.\cite{10.1016/j.commatsci.2012.10.028}
This demonstrated that routines and methods developed for treating CIF files can be used in this application to adsorption data.
Furthermore, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the the fastest open-source CIF parser.\cite{gemmi}
We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
This is a very simple implementation and it is hoped that future versions, following the cooperation of several manufactures, could result in to routines to parse the information directly from binary data used by the instruments.

@@

\section{Summary and perspective}
The rise in interest of new advanced adsorbents for application in promising areas has followed a lack of detailed and open reporting of experimental or even computational studies.
This report details the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
The AIF is a flexible, general and easily extended free-format archive file and is readily human and machine readable--- simple to edit using a basic text editor or parse for database curation.
This format represents the first steps to an open adsorption data format.
An open format sorely needed for the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials.

>>>>

This simple program will parse the output data to find data items detailed in the AIF dictionary.
These data items are converted to the appropriate units and the isotherm is split into the adsorption and desorption parts.
Subsequently an AIF is produced using \textit{gemmi} CIF routines.\cite{gemmi}
As a consequence routines and methods developed for treating CIF files can be used in this application to adsorption data.
For example produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the the fastest open-source CIF parser.\cite{gemmi}
We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
This is a very simple implementation and it is hoped that future versions, following the cooperation of several manufactures, could result in to routines to parse the information directly from binary data used by the instruments.

@@

\section{Summary and perspective}
There is a current need to a universal format for archiving adsorption data.
This is pertinent for the development of detailed databases of information that can play an important role in further materials design.\cite{10.1021/acs.chemmater.9b03376}
This report details the specification of a new standard file, named AIF, based on the self-defining text archive and retrieval (STAR) procedure, inspired by similar universal and evolving formats currently used in the larger scientific community.
The AIF is importantly an easily extended free-format archive file that can be both human and machine readable.
This format represents the first steps to an open adsorption data format and the community is encouraged to take up this format.
